О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-09 pps-linear-bound/pps-linear-lower-bound.tex
Remarks on the construction

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{construction}[theorem]{Construction}

@@

TODO: $k=2$ and construction from~\cite{harborth1993upper}

TODO: remark on taking $k=1$.

>>>>

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{construction}[theorem]{Construction}
\newtheorem{remark}[theorem]{Remark}

@@

TODO: get rid of $H_{1,2}$; write signs $\pm$ to $M_J$; recalculate the cardinality; allow $k=1$.

\begin{remark}
	Taking $k=1$ for Construction~\ref{con:planar_set_with_minimeter_1},
	we obtain 3 points which form a right triangle with side length 1.
	This triangle is obviously the optimal set in $\mathfrak{M}(2,3)$.
\end{remark}

\begin{remark}
	Taking $k=2$ for Construction~\ref{con:planar_set_with_minimeter_1},
	we obtain the optimal set in $\mathfrak{M}(2,5)$ presented in~\cite[Fig. 1]{harborth1993upper}.
	If we truncate one point from it,
	then we get on of the two optimal sets in $\mathfrak{M}(2,4)$.
\end{remark}

\begin{hypothesis}
	Every set $M\in\mathfrak{M}(2,n)$, $n\geq 6$, such that for some $M_1,M_2$ equality $|M_1 - M_2|=1$ holds,
	is not optimal.
\end{hypothesis}
